Experiments with Synthetic Data

### 2022-07-19 dev/notebooks/synthetic.qmd
code for experiment running, including with mutli-threading

```{julia}
# Models:
models = (Bayesian=M_laplace, Plugin=M)
# Generators:
generators = (
    Bayesian=GreedyGenerator(loss=:logitbinarycrossentropy), 
    Plugin=GenericGenerator(loss=:logitbinarycrossentropy,ϵ=0.01)
)
```

@@

```{julia}
cb = false
γ = 0.75
mod = M_laplace
gen = generators[:Plugin]
plt_original = plot(mod,counterfactual_data;zoom=0,colorbar=false,title="(a)")
```

@@

```{julia}
using AlgorithmicRecourseDynamics.Experiments
# Variables:
μ = [0.05,0.1,0.25]
γ = [0.50,0.75,0.9]
grid_ = Experiments.GridVariables(models, generators, μ, γ)
n_rounds = 5
n_folds = 1
target = 1.0
T = 1000
```

>>>>

```{julia}
# Models:
models = (Bayesian=M_laplace, Plugin=M)
# Generators:
generators = (
    Greedy=GreedyGenerator(loss=:logitbinarycrossentropy), 
    Generic=GenericGenerator(loss=:logitbinarycrossentropy),
    REVISE=REVISEGenerator(loss=:logitbinarycrossentropy)
)
```

@@

```{julia}
cb = false
γ = 0.75
mod = M_laplace
gen = generators[:Greedy]
plt_original = plot(mod,counterfactual_data;zoom=0,colorbar=false,title="(a)")
```

@@

```{julia}
using AlgorithmicRecourseDynamics.Experiments
using AlgorithmicRecourseDynamics.Experiments: Experiment
target = 1.0
experiment = Experiment(counterfactual_data, target, models, generators)
```

```{julia}
# Variables:
μ = 0.1
γ = 0.75
n_rounds = 10
n_folds = 5
T = 1000
```

```{julia}
run_experiment(experiment; n_rounds=n_rounds, μ=μ, n_folds=n_folds, γ=γ, T=T)
```
